---
title: "Prevention through Design (PtD) to Make Solar-Ready Houses Safe for Solar installers"
author:
  - Hyun Woo Lee, John Gambatese, Yohan Min
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::pdf_document2:

bibliography: references.bib
csl: "journal-of-construction-engineering-and-management.csl" # Insert path for the bib-style
header-includes:
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage[fontsize=11pt]{scrextend}
---

```{r setup, include=FALSE, fig.align="center"}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(lubridate)
library(readxl)
library(kableExtra)
library(knitr)
load("../../data/sur.Rdata")
```


Case Study 4 represents a common residential house not solar-ready. It was told that it took about 5 days to install the solar system in this house. This house has several obstructions on the roof, which is complex in shape, thus solar modules had to be installed in the multi-split zones. In particular, south facing roof area was not enough to have all the modules, thus the modules had to be installed on the other sides, on the east facing and west facing roofs. Thirteen modules were installed on west, twelve on south and ten on east. Even the solar modules installed on the south facing root had to be split into three zones (two, four and six modules separately). The roof pitch is 8/12 and roofing material is composition, which led to roof penetration during installation. The roof shape made hard to secure access pathways around the solar modules. Conduit for the solar system is run outside wall. Tie-offs were installed when the work for the rooftop solar had started. The characteristics of the house is typical around the area. The comparisons of the case studies are in the table below.


```{r warning=F, message=F}
data <- read_excel("../case/compare.xlsx", sheet = 1,col_names = TRUE)[2:6][1:22,]
# View(data)

kable(data, "latex", booktabs = T) %>%
  pack_rows("Solar zone", 2, 10, latex_gap_space = "1em") %>%
  pack_rows("Installation", 11, 16, latex_gap_space = "1em") %>%
  pack_rows("Solar system", 17, 22, latex_gap_space = "1em")

```
